Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-01-29 analysis/paper/London_HauloutBeahvior.Rmd
improvements to example actogram figure

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="Haul-out behavior observations recorded by a bio-logger deployed on a ribbon seal over two years during the months of March, April, and May. This actogram plot represents the transmitted hourly percent-dry values. Not all data during a deployment are reliably transmitted from the bio-logger and since data are transmitted in 24-hour chunks occasional missing days are present in the record. Here, missing data that were not successfully recieved from the device are represented as empty rectangles."}
Tags that fall off due to molt, attachment failure, or seal mortality and remain
on ice or land may continue to send data to satellites; i.e., a detached
bio-logger that is dry (either on ice or land) will record and transmit data
suggesting the seal is hauled out. Therefore, end times of each deployment were
identified by examining bio-logger locations, percent-dry records, and dive
behavior (if available) to determine when bio-loggers ceased providing data
consistent with seal behavior. For example, a data record that ends with several
consecutive days (~10+ days) of 100% dry observations and with locations
indicating the tag was on land would be truncated to not include the final
stretch of 100% dry observations. The vast majority of deployments end with the
device detaching in the water and the deployment end date is obvious. There is
no perfect algorithm for identifying deployment end dates and each deployment in
question must be considered separately. While not perfect, we are confident our
reliance on expert opinion and examination of multiple data streams provides the
best option. Data outside of the deployment start and end times were discarded
prior to analysis.

@@

p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  ggtitle("Example percent-dry actogram from bio-logger data",
          subtitle = "Observation records shown are from a single ribbon seal across a two year deployment.") +
  xlab("day of month") + ylab("hour (UTC)")

>>>>

Tags that fall off due to molt, attachment failure, or seal mortality and remain
on ice or land may continue to send data to satellites; i.e., a detached
bio-logger that is dry (either on ice or land) will record and transmit data
suggesting the seal is hauled out. Therefore, end times of each deployment were
identified by examining bio-logger locations, percent-dry records, and dive
behavior (if available) to determine when bio-loggers ceased providing data
consistent with seal behavior. For example, a data record that ends with several
consecutive days (~10+ days) of 100% dry observations and with locations
indicating the tag was on land would be truncated to not include the final
stretch of 100% dry observations. The vast majority of deployments end with the
device detaching in the water and the deployment end date is obvious. There is
no perfect algorithm for identifying deployment end dates and each deployment in
question must be considered separately. While not perfect, we are confident our
reliance on expert opinion and examination of multiple data streams provides the
best option. Data outside of the deployment start and end times were discarded
prior to analysis.

(ref:examplePlotCaption) **Example percent-dry actogram from bio-logger data**
\linebreak Haul-out behavior observations recorded by a bio-logger deployed on a
ribbon seal over two years during the months of March, April, and May. This
actogram plot represents the transmitted hourly percent-dry values. Not all data
during a deployment are reliably transmitted from the bio-logger and since data
are transmitted in 24-hour chunks occasional missing days are present in the
record. Here, missing data that were not successfully recieved from the device
are represented as empty rectangles.

```{r examplePlot, include=TRUE, fig.id="examplePlot", fig.cap="(ref:examplePlotCaption)"}

@@

p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  theme(panel.spacing = unit(0,"line")) +
  xlab("day of month") + ylab("hour (UTC)")
